### 2016-01-25 mcmc.tex
problem tweaks

\begin{problem}
Look up (or choose) definitions for the mean, variance, skewness,
and kurtosis of a distribution.
Also look up or compute the analytic values of these for a top-hat
(uniform) distribution.
Write a computer program that uses some standard package (such as
\project{numpy}\note{HOGG CITE NUMPY}) to generate $K$ random numbers
$x$ from a uniform distribution in the interval $0<x<1$.
Now use those $K$ numbers to compute a the sampling estimate of the
mean, variance, skewness, and kurtosis (four estimates)
Make four plot of these four estimates as a function of $\ln K$, for
$K=2^n$ for $n=8$ up to $n=20$ (that is, $K=256$, $K=512$, and so on
up to $K=1048576$).
Over-plot the analytic answers.
What can you conclude?
\end{problem}

>>>>

\begin{problem}
Look up (or choose) definitions for the mean, variance, skewness,
and kurtosis of a distribution.
Also look up or compute the analytic values of these four statistics
for a top-hat (uniform) distribution.
Write a computer program that uses some standard package (such as
\project{numpy}\note{HOGG CITE NUMPY}) to generate $K$ random numbers
$x$ from a uniform distribution in the interval $0<x<1$.
Now use those $K$ numbers to compute a the sampling estimate of the
mean, variance, skewness, and kurtosis (four estimates)
Make four plot of these four estimates as a function of $1/K$ or
perhaps $\log_2 K$, for $K=4^n$ for $n=1$ up to $n=10$ (that is,
$K=4$, $K=16$, and so on up to $K=1048576$).
Over-plot the analytic answers.
What can you conclude?
\end{problem}
